Authors Response to Reviewer's Comments

### 2023-10-01 manuscript/manuscriptRW.Rmd
r2 comment 22/ 24

In the models used here, the overall complexity in the regeneration modules varies considerably. Following @bugmann2022, we can classify seven models (iLand, PICUS, LandClim, ForCEEPS, LPJ-GUESS, ForClim and TreeMig) as having rather high complexity in their regeneration modules (mean regeneration formulation complexity across all processes \>0, Table \@ref(tab:tableModels)). Two models, ForClim and ForCEEPS, were used here with two alternative variants of regeneration. ForClim variant 1 [@bugmann1996] is based on a recruitment module that adheres closely to the concept introduced by @botkin1972, whereas ForClim variant 11 is adopting a different approach where individual species properties and their relation to the environment are important [@huber2020]. These two model variants allow us to evaluate a more process-based and complex module (variant 11) against a simple module (variant 1), while the rest of the model structure is identical. Similarly, the two ForCEEPS variants allow us to isolate the importance of the canopy feedback (i.e., simulated actual composition and relative abundance of species in the plot) via seed trees for the quantity and quality (e.g., diversity and composition) of simulated regeneration, as one variant includes this feedback whereas the other does not.

>>>>

In the models used here, the overall complexity in the regeneration modules varies considerably. Following @bugmann2022, we can classify seven models (iLand, PICUS, LandClim, ForCEEPS, LPJ-GUESS, ForClim and TreeMig) as having rather high complexity in their regeneration modules (mean regeneration formulation complexity across all processes \>0, Table \@ref(tab:tableModels)). Two models, ForClim and ForCEEPS, were used here with two alternative variants of regeneration. ForClim variant 1 [@bugmann1996] is based on a recruitment module that adheres closely to the concept introduced by @botkin1972 which is an environmental filter considering species specific thresholds of light availability and climatic variables. Whereas ForClim variant 11 is adopting a slightly more complex approach where individual species properties and their relation to the environment are represented gradually along with the relative suitability of different species (i.e., competition among tree species) [@huber2020]. These two model variants allow us to evaluate a more process-based and complex module (variant 11) against a simple module (variant 1), while the rest of the model structure is identical. Similarly, the two ForCEEPS variants allow us to isolate the importance of the canopy feedback (i.e., simulated actual composition and relative abundance of species in the plot) via seed trees for the quantity and quality (e.g., diversity and composition) of simulated regeneration, as one variant includes this feedback whereas the other does not.

### 2023-10-01 manuscript/review/authorsResponse.qmd
r2 comment 22/ 24

We agree with the reviewer's comment that there are other forest inventory data networks outside Central Europe even on forest reserves that could provide this sort of data. However, the EuFoRIa network is indeed novel and unprecedented network in Central Europe.

@@

>>>>

We agree with the reviewer's comment that there are other forest inventory data networks outside Central Europe even on forest reserves that could provide this sort of data. However, within Europe no such data existed before. The research network (EuFoRIa) was established in 2019 and therefor is in fact novel, and within Europe such data is also without precedence.

Yet we acknowledge that our statement needs to be put in a European context much clearer. We hope that our adjustments to the text resolve the exaggeration of our initial formulation.

@@

​

​

​

​

​

​

​

​

​

​
